### 2024-01-09 paper/main_4.2_volcano_plots.tex
main SI prefix in cross-ref

Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in \cref{main_fig3:volcano}b and Supplementary \cref{si_fig13:n-gra_ptable} to \cref{si_fig17:C2N_ptable}.
Our analyses do not reveal consistent trends within groups or periods, nor did they exhibit evident patterns across substrates.
These observations suggest intricate interactions between supported metal atoms and substrates.
The absence of straightforward trends underscores the need for nuanced explorations in understanding these interactions like the CNN model.

>>>>

Additionally, we mapped the theoretical limiting potentials of the analyzed catalyst candidates onto periodic tables, shown in \cref{main_fig3:volcano}b and Supplementary \cref{si_fig13:n-gra_ptable} to Supplementary \cref{si_fig17:C2N_ptable}.
Our analyses do not reveal consistent trends within groups or periods, nor did they exhibit evident patterns across substrates.
These observations suggest intricate interactions between supported metal atoms and substrates.
The absence of straightforward trends underscores the need for nuanced explorations in understanding these interactions like the CNN model.
